%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green}                              % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{John Charles}{Boyington}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{777 Hoopes Ave., Apt. J104}{Idaho Falls, ID 83401}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{(785)543~4260}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{+2~(345)~678~901}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{mjcb@ksu.edu}                               % optional, remove / comment the line if not wanted
%\homepage{www.johndoe.com}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Hallmark Cards, Inc.}{2501 McGee Trafficway\\Kansas City, MO 64108}
\date{July 01, 2019}
\opening{Dear Sir or Madam,}
\closing{Yours faithfully,}
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

%%% intro paragraph (summarize what is the job, why i am interested, and what makes me a good fit)

% who am i, because that fits
As a generalist constantly seeking new disciplines to study and ways to challenge myself, I would like to express my serious interest in your Data Analyst position.
I am currently finishing my masters in Nuclear Engineering from Kansas State University and while there, I've spent the last two and a half years innovating in the nuclear realm, applying artificial intelligence to solve complex optimization problems and collecting and visualizing modestly-sized datasets to study reactor physics.
I believe that as a data analyst, I could continue to grow my repertoire of professional skills, while simultaneously proving to Hallmark to be an indispensible asset through my wide set of mathematic and computational skills, unique perspectives, highly adaptable persona, and strong ability to communicate.


%%% body paragraphs (list the responsibility, project i participated in, skills i acquired, and impact i had)
I've never been satisfied with completing the bare minimum requirements for any of my graduate school tasks .
This is exempified by my Principles of Artificial Intelligence final class project, where I sought an open problem on the forefront of machine learning research, studied multiple papers and methods including some from Facebook and DeepMind's own research teams, taught myself TensorFlow, developed a game-playing agent, and merited remarks from the class professor claiming I ``went well beyond the requirements of the class'' and ``intuited methods that wouldn't be covered until his advanced AI class''.
My ability to quickly learn new software, methods, and problem domains would allow me to thrive in your work environment.
I view large datasets like new continents to be explored and am highly motivated by new and interesting problems.

Through graduate school, I have amassed around three years experience coding in Python and have flexed the language in a variety of ways to solve problems.
I have TA'd for three semesters for both undergraduate and graduate level numerical methods courses and now have acquired much expertise in scientific computing.

%%% closing paragraph (re-emphasize interest in position, why i'm passionate about company, why i'd make a good fit)

A close friend and Hallmark intern, Benjamin Heath, has discussed with me the excellent work culture at Hallmark, mentioning that it's likely unmatched in the Kansas City area, and has further deepened my interest in working for you.
%%% call to action
I believe that my unique combination of skills is rare and valuable, and coupled with my desire to innovate for you, I very much look forward to the possibility for employment.
Please contact me if you require any further details regarding my application or have any questions for me.

\makeletterclosing

\end{document}


%% end of file `template.tex'.
